### 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
SNL location corrected

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.  Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day. Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch. An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C. Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Arvada, Colorado, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}. In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.

@@

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simplified counter-flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

\begin{figure}[H] 
    %[htb]
    \widefigure
    \includegraphics[width=10 cm]{Definitions/csp.pdf}
    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and csp black box heat input\label{csp}}
\end{figure}
% \begin{paracol}{2}
% \linenumbers
% \switchcolumn

>>>>

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures. Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.  Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.
A CSP has an array of mirrors concentrating solar rays towards a receiver to generate thermal energy therefore causing a dependency on weather conditions and time of day. Previous research has modeled CSP technology as the thermal source for Brayton sCO$_2$ cycles with promising results in efficiency gains and high temperature thermal energy storage \cite{turchi_2013, iverson_2013, ho_2015, wang_2018, neises_2020}. Thermal energy gathered from the CSP is stored in thermal energy storage which is dispatched into the sCO$_2$ Brayton cycle when grid demand increases. With a comparable temperature to the hot TES, 560 $^{\circ}$C, a LFR is capable of transferring heat to thermal storage for later dispatch. An LFR uses fission reactions to heat a heat transfer fluid, in this case liquid lead, to temperatures of 650 $^{\circ}$C. Nuclear sCO$_2$ Brayton cycles have been studied with similar gains in efficiency seen in CSP sCO$_2$ Brayton cycles \cite{ dostal_2004, luo_2020}. Physical testing of simple sCO$_2$ Brayton cycles is researched at Sandia National Labs in Albuquerque, NM, with break-even conditions, where the turbine produces enough power to offset compressor demand, being achieved \cite{wright_2011}. In addition to break-even conditions, research from the Supercritical CO$_2$ Brayton Cycle Integral Experiment Loop, in Korea Atomic Energy Institute, achieved electrical generation in a simple sCO$_2$ Brayton cycle \cite{cha_2016}.

@@

\end{paracol}
\begin{figure}[h]
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simplified counter-flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

\begin{figure}[h] 
    %[htb]
    \widefigure
    \includegraphics[width=10 cm]{Definitions/csp.pdf}
    \caption{Diagram for CSP cycle with cold and hot thermal energy storage, pumps, and csp black box heat input\label{csp}}
\end{figure}
% \begin{paracol}{2}
% \linenumbers
% \switchcolumn
